### 2020-05-25 system-model.tex
:art: Fix achievable rate

	\begin{subsection}{Receive Signal}
		The RF signal received by user $k$ captures the contribution of information and power waveforms through both direct and reflective links as
		\begin{equation}\label{eq:y_k}
			y_k(t)=\Re\left\{\sum_{n=1}^N{h_{{k,n}}}\left(\sum_{j=1}^K{w_{I,j,n}\tilde{x}_{I,j,n}(t)}+w_{P,n}\right){e^{j2{\pi}{f_n}{t}}}\right\}
		\end{equation}
	\end{subsection}

	\begin{subsection}{Information Decoder}
		One major benefit of using proposed waveform is that the deterministic power term $y_{P,k}(t)$ bears no information and creates no interference to the modulated information term $y_{I,k}(t)$. Hence, each user treats the information signals from other users as interference such that the SINR at subband $n$ of user $k$ is
		\begin{equation}\label{eq:gamma_{k,n}}
			\gamma_{k,n}=\frac{(1-\rho)(h_{k,n}w_{I,k,n})(h_{k,n}w_{I,k,n})^*}{\sum_{j=1,j{\ne}k}^K{(1-\rho)(h_{k,n}w_{I,j,n})(h_{k,n}w_{I,j,n})^*+\sigma_n^2}}
		\end{equation}
		where $\sigma_n^2$ is the sum variance of the Gaussian noise at the RF-band and those introduced during the RF-to-BB conversion on subband $n$. Therefore, the achievable rate of user $k$ is expressed as
		\begin{equation}\label{eq:R_k}
			R_k(\boldsymbol{W}_I,\boldsymbol{\Theta}_0,\rho)=\sum_{n=1}^N{\log_2(1+\gamma_{k,n})}
		\end{equation}
		A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:R_k} is always achievable with or without waveform cancellation, through either subtracting the deterministic power component or constructing a translated codebook.
	\end{subsection}

	\begin{subsection}{Energy Harvester}
		Note that the information and power component $y_{I,k}(t)$ and $y_{P,k}(t)$ have different influence on the output DC current. Consider a nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2018b,Clerckx2016a}, which highlights the dependency of the harvester output DC current on the received waveform as
		\begin{equation}\label{eq:i_k}
			i_k\approx\sum_{i=0}^{\infty}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y_k(t)^i\right\}}\right\}

@@

		where $R_{\text{ant}}$ is the impedance of the receive antenna, $k_0'=i_s(e^{-i_kR_{\text{ant}}/nv_t}-1)$, $k_i'=i_se^{-i_kR_{\text{ant}}/nv_t}/i!(nv_t)^i$ for $i=1,\dots,\infty$, $i_s$ is saturation current, $n$ is diode ideality factor, $v_t$ is thermal voltage. Once the composite channel response $h_{k,n}$ is fixed, the corresponding information and power weight $w_{I,k,n}$, $w_{P,k,n}$ are thus optimized such that the randomness comes from the input distribution $\tilde{x}_{k,n}$. Therefore, we first extract the DC component based on $h_{k,n}$, $w_{I,k,n}$, $w_{P,k,n}$ by $\mathcal{A}\left\{.\right\}$ and then take the expectation over $\tilde{x}_{k,n}$ by $\mathcal{E}\left\{.\right\}$. With the assumption of evenly spaced frequencies, $\mathcal{E}\left\{y^i(t)\right\}=0$ for odd $i$ and the related terms has zero contribution to DC components. \cite{Clerckx2016a} also demonstrated that to maximize $i_k$, it suffices to maximize the monotonic target function truncated to the $n_0$ order
			z_k(\boldsymbol{W}_I,\boldsymbol{W}_P,\boldsymbol{\Theta}_0,\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_k(t)^i\right\}\right\}}
		where $k_i=i_s/i!(nv_t)^i$. We take $n_0=4$ to investigate the fundamental impact of diode nonlinearity on power transfer. Note that $\mathcal{E}\{\mathcal{A}\{y_{I,k}(t)y_{P,k}(t)\}\}=\mathcal{E}\{\mathcal{A}\{y_{I,k}^3(t)y_{P,k}(t)\}\}=\mathcal{E}\{\mathcal{A}\{y_{I,k}(t)y_{P,k}^3(t)\}\}=0$, $\mathcal{E}\{\mathcal{A}\{y_{I,k}^2(t)y_{P,k}^2(t)\}\}=\mathcal{A}\{\mathcal{E}\{y_{I,k}^2(t)\}\}\mathcal{A}\{y_{P,k}^2(t)\}$, and the remaining terms are expressed by \ref{eq:E{A{y_{I,k}**2}}} -- \ref{eq:A{y_{P,k}**4'}}. It is noteworthy that modulation provides a power gain to the nonlinear terms in the output DC current as $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^4\right\}=2$.

@@

				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{(h_{k,n}w_{I,j_1,n})(h_{k,n}w_{I,j_2,n})^*}\label{eq:E{A{y_{I,k}**2}}}                                                                                                                                                                        \\
				%  & =\frac{1}{2}\sum_n{{\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}}}                                                                                                                                                                                                      \\
				 & =\frac{1}{2}\sum_n{h_{k,n}h_{k,n}^*{\boldsymbol{w}_{I,n}^H}{\boldsymbol{J}_{K}}{\boldsymbol{w}_{I,n}}}                                                                                                                                                                         \\
				%  & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{\left[w_{I,j_1,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]\left[w_{I,j_2,n}(h_{D,n,k}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]^*}                                                                                                                        \\

@@

				 & =\frac{3}{4}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{I,{j_1},{n_1}})(h_{k,{n_2}}w_{I,{j_2},{n_2}})(h_{k,{n_3}}w_{I,{j_3},{n_3}})^*(h_{k,{n_4}}w_{I,{j_4},{n_4}})^*}                       \\
				%  & = \frac{3}{4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{({\boldsymbol{w}_{I,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{I,n_1}})({\boldsymbol{w}_{I,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{I,n_2}})} \\
				 & =\frac{3}{4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}(\boldsymbol{w}_{I,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_1})(\boldsymbol{w}_{I,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_2})} \\
				%  & =\frac{3}{4}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}\left[w_{I,{j_1},{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]\left[w_{I,{j_2},{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]\nonumber \\
				%  & \quad\left[w_{I,{j_3},{n_3}}(h_{D,k,n_3}+\boldsymbol{h}_{R,k,n_3}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_3})\right]^*\left[w_{I,{j_4},{n_4}}(h_{D,k,n_4}+\boldsymbol{h}_{R,k,n_4}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_4})\right]^*                                                                                                                           \\

@@

				 & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{(h_{k,n}w_{P,j_1,n})(h_{k,n}w_{P,j_2,n})^*}                                                                                                                                                                                                   \\
				%  & = \frac{1}{2}\sum_n{{\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}}}                                                                                                                                                                                                     \\
				 & =\frac{1}{2}\sum_n{h_{k,n}h_{k,n}^*{\boldsymbol{w}_{P,n}^H}{\boldsymbol{J}_{K}}{\boldsymbol{w}_{P,n}}}                                                                                                                                                                         \\
				%  & =\frac{1}{2}\sum_{j_1,j_2}\sum_n{\left[w_{P,j_1,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]\left[w_{P,j_2,n}(h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})\right]^*}                                                                                                                        \\

@@

				 & =\frac{3}{8}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{P,{j_1},{n_1}})(h_{k,{n_2}}w_{P,{j_2},{n_2}})(h_{k,{n_3}}w_{P,{j_3},{n_3}})^*(h_{k,{n_4}}w_{P,{j_4},{n_4}})^*}                       \\
				%  & =\frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{({\boldsymbol{w}_{P,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{P,n_1}})({\boldsymbol{w}_{P,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{P,n_2}})}  \\
				 & =\frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}(\boldsymbol{w}_{P,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_1})(\boldsymbol{w}_{P,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_2})}
				\label{eq:A{y_{P,k}**4'}}
				%  & =\frac{3}{8}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}\left[w_{P,{j_1},{n_1}}(h_{D,k,n_1}+\boldsymbol{h}_{R,k,n_1}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_1})\right]\left[w_{P,{j_2},{n_2}}(h_{D,k,n_2}+\boldsymbol{h}_{R,k,n_2}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_2})\right]\nonumber \\
				%  & \quad\left[w_{P,{j_3},{n_3}}(h_{D,k,n_3}+\boldsymbol{h}_{R,k,n_3}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_3})\right]^*\left[w_{P,{j_4},{n_4}}(h_{D,k,n_4}+\boldsymbol{h}_{R,k,n_4}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n_4})\right]^*\label{eq:A{y_{P,k}**4'}}

@@

		Therefore, \ref{eq:z_k} reduces to \ref{eq:z_k_truncated}.

@@

					% z_k(\boldsymbol{W}_I,\boldsymbol{W}_P,\boldsymbol{\Theta},\rho)

@@

					&={k_2}{\rho}{R_{\text{ant}}}\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)+{k_4}{\rho^2}{R_{\text{ant}}^2}\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)\\
					% &=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{{\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}}+{\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}}}\\
					% &\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{2({\boldsymbol{w}_{I,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{I,n_1}})({\boldsymbol{w}_{I,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{I,n_2}})+({\boldsymbol{w}_{P,n_3}^H}{\boldsymbol{h}_{k,n_3}^*}{\boldsymbol{h}_{k,n_1}^T}{\boldsymbol{w}_{P,n_1}})({\boldsymbol{w}_{P,n_4}^H}{\boldsymbol{h}_{k,n_4}^*}{\boldsymbol{h}_{k,n_2}^T}{\boldsymbol{w}_{P,n_2}})}\\
					% &\quad+\frac{3}{2}{k_4'}{\rho^2}{R_{\text{ant}}^2}\sum_n({\boldsymbol{w}_{I,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{I,n}})({\boldsymbol{w}_{P,n}^H}{\boldsymbol{h}_{k,n}^*}{\boldsymbol{h}_{k,n}^T}{\boldsymbol{w}_{P,n}})\\
					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{h_{k,n}h_{k,n}^*(\boldsymbol{w}_{I,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{I,n}+\boldsymbol{w}_{P,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{P,n})}\\
					&\quad+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}\left(2(\boldsymbol{w}_{I,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_1})(\boldsymbol{w}_{I,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_2})+(\boldsymbol{w}_{P,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_1})(\boldsymbol{w}_{P,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_2})\right)}\\
					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n{h_{k,n}^2h_{k,n}^{*2}(\boldsymbol{w}_{I,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{I,n})(\boldsymbol{w}_{P,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{P,n})}

>>>>

	\begin{subsection}{Receive Signal}
		The RF signal received by user $k$ captures the contribution of information and power waveforms through both direct and reflective links as
		\begin{equation}\label{eq:y_k}
			y_k(t)=\Re\left\{\sum_{n=1}^N{h_{{k,n}}}\left(\sum_{j=1}^K{w_{I,j,n}\tilde{x}_{I,j,n}(t)}+w_{P,n}\right){e^{j2{\pi}{f_n}{t}}}\right\}
		\end{equation}
		which can be divided into
		\begin{align}\label{eq:y_{I/P,k}}
			y_{I,k}(t) & = \Re\left\{\sum_{j=1}^K\sum_{n=1}^N{h_{{k,n}}}{w_{I,j,n}\tilde{x}_{I,j,n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\}\\
			y_{P,k}(t) & = \Re\left\{\sum_{n=1}^N{h_{{k,n}}}w_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}
		\end{align}
	\end{subsection}

	\begin{subsection}{Information Decoder}
		% ? OFDM interference
		One major benefit of the superposed waveform is that the power component $y_{P,k}(t)$ creates no interference to the information component $y_{I,k}(t)$. Hence, the achievable rate of user $k$ is
		\begin{equation}\label{eq:R_k}
			R_k(\{\boldsymbol{w}_{I,k}\},\boldsymbol{\phi},\rho)=\sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert h_{k,n}w_{I,k,n} \rvert^2}{\sigma_n^2}\right)}
		\end{equation}
		where $\sigma_n^2$ is the variance of the noise at RF band and during RF-to-BB conversion on tone $n$. Rate \ref{eq:R_k} is achievable with either waveform cancellation or translated demodulation \cite{Clerckx2018b}.
	\end{subsection}

	\begin{subsection}{Energy Harvester}
		Consider a nonlinear diode model based on the Taylor expansion of a small signal model \cite{Clerckx2016a,Clerckx2018b}, which highlights the dependency of harvester output DC current on the received waveform of user $k$ as
		\begin{equation}\label{eq:i_k}
			i_k(\{\boldsymbol{w}_{I,k}\},\{\boldsymbol{w}_{P,k}\},\boldsymbol{\phi},\rho)\approx\sum_{i=0}^{\infty}{k_i'}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}\mathcal{E}\left\{{\mathcal{A}\left\{y_k(t)^i\right\}}\right\}
		\end{equation}
		where $R_{\text{ant}}$ is the impedance of the receive antenna, $k_0'=i_s(e^{-i_kR_{\text{ant}}/nv_t}-1)$, $k_i'=i_se^{-i_kR_{\text{ant}}/nv_t}/i!(nv_t)^i$ for $i=1,\dots,\infty$, $i_s$ is saturation current, $n$ is diode ideality factor, $v_t$ is thermal voltage. For a fixed channel and waveform, $\mathcal{A}\left\{.\right\}$ extracts the DC component of the received signal while $\mathcal{E}\left\{.\right\}$ covers the expectation over $\tilde{x}_{I,k,n}$.

		With the assumption of evenly spaced frequencies, we have $\mathcal{E}\left\{y_k(t)^i\right\}=0 \ \forall i \ \mathrm{odd}$ such that the related terms has no contribution to DC components. For simplicity, we truncate the infinite series to the $n_0$-th order. Maximizing a truncated \ref{eq:i_k} is equivalent to maximizing a monotonic function \cite{Clerckx2016a}
			z_k(\{\boldsymbol{w}_{I,k}\},\{\boldsymbol{w}_{P,k}\},\boldsymbol{\phi},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_k(t)^i\right\}\right\}}

@@

		where $k_i=i_s/i!(nv_t)^i$. We choose $n_0=4$ to investigate the fundamental impact of diode nonlinearity on energy harvest. Nonzero terms are given in \ref{eq:z_k_terms_begin} -- \ref{eq:z_k_terms_end}. Note that $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^2\right\}=1$ and $\mathcal{E}\left\{\lvert\tilde{x}_{k,n}\rvert^4\right\}=2$, which can be interpreted as a modulation gain in the nonlinear terms of the output DC current. On top of this, the current expression \ref{eq:z_k} reduces to \ref{eq:z_k_truncated}.

@@

				& = \frac{1}{2}\sum_{j_1,j_2}\sum_n{(h_{k,n}w_{I,j_1,n})(h_{k,n}w_{I,j_2,n})^*}\label{eq:z_k_terms_begin}\\
				& = \frac{1}{2}\sum_n{h_{k,n}h_{k,n}^*{\boldsymbol{w}_{I,n}^H}{\boldsymbol{J}_{K}}{\boldsymbol{w}_{I,n}}}\\

@@

				& = \frac{3}{4}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{I,{j_1},{n_1}})(h_{k,{n_2}}w_{I,{j_2},{n_2}})(h_{k,{n_3}}w_{I,{j_3},{n_3}})^*(h_{k,{n_4}}w_{I,{j_4},{n_4}})^*}\\
				& = \frac{3}{4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}(\boldsymbol{w}_{I,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_1})(\boldsymbol{w}_{I,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_2})}\\

@@

				& = \frac{1}{2}\sum_{j_1,j_2}\sum_n{(h_{k,n}w_{P,j_1,n})(h_{k,n}w_{P,j_2,n})^*}\\
				& = \frac{1}{2}\sum_n{h_{k,n}h_{k,n}^*{\boldsymbol{w}_{P,n}^H}{\boldsymbol{J}_{K}}{\boldsymbol{w}_{P,n}}}\\

@@

				& = \frac{3}{8}\sum_{j_1,j_2,j_3,j_4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{P,{j_1},{n_1}})(h_{k,{n_2}}w_{P,{j_2},{n_2}})(h_{k,{n_3}}w_{P,{j_3},{n_3}})^*(h_{k,{n_4}}w_{P,{j_4},{n_4}})^*}\\
				& = \frac{3}{8}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}(\boldsymbol{w}_{P,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_1})(\boldsymbol{w}_{P,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_2})}\label{eq:z_k_terms_end}

@@

@@

@@

					& = {k_2}{\rho}{R_{\text{ant}}}\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)+{k_4}{\rho^2}{R_{\text{ant}}^2}\left(\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^4(t)\right\}\right\}+\mathcal{A}\left\{y_{P,k}^4(t)\right\}+6\mathcal{E}\left\{\mathcal{A}\left\{y_{I,k}^2(t)\right\}\right\}\mathcal{A}\left\{y_{P,k}^2(t)\right\}\right)\\
					& = \frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{h_{k,n}h_{k,n}^*(\boldsymbol{w}_{I,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{I,n}+\boldsymbol{w}_{P,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{P,n})}\\
					& \quad+ \frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{h_{k,n_3}^*h_{k,n_1}h_{k,n_4}^*h_{k,n_2}\left(2(\boldsymbol{w}_{I,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_1})(\boldsymbol{w}_{I,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{I,n_2})+(\boldsymbol{w}_{P,n_3}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_1})(\boldsymbol{w}_{P,n_4}^H\boldsymbol{J}_K\boldsymbol{w}_{P,n_2})\right)}\\
					& \quad+ \frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n{h_{k,n}^2h_{k,n}^{*2}(\boldsymbol{w}_{I,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{I,n})(\boldsymbol{w}_{P,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{P,n})}
